Gusto: a toolkit for compatible finite element dynamical cores

### 2023-07-25 source/paper.tex
small changes

\begin{align}
  \pp{\MM{u}}{t} + 
  (\MM{u}\cdot\nabla)\MM{u} +
  f\hat{\MM{k}}\times \MM{u} + \nabla p + b\hat{\MM{k}} & = 0, \\
  \pp{p}{t} + c^2\nabla\cdot\MM{u} & = 0, \\
  \pp{b}{t} + \MM{u}\cdot\nabla(b) & = 0, \\
\end{align}

@@

\begin{align}
  \pp{\MM{u}}{t} + 
  (\MM{u}\cdot\nabla)\MM{u} +
  f\hat{\MM{k}}\times \MM{u} + c_p\theta\nabla \Pi + g\hat{\MM{k}} & = 0, \\
  \pp{\rho}{t} + \nabla\cdot(\MM{u}\rho) & = 0, \\
  \pp{\theta}{t} + \MM{u}\cdot\nabla\theta & = 0, \\
  \Pi^{(1-\kappa)/\kappa} = \frac{R}{p_0}\rho\theta, & 
\end{align}

@@

\section{Results}
\label{sec: results}
The aim of this section is to present a selection of results that
demonstrate the tools available in Gusto, such as the choice of grids,
order of finite element fucntion spaces, different spatial
discretisation options, timestepping schemes and physics. The
numerical properties of these configurations (convergence, stability,
accuracy and efficiency) have either been demonstrated elsewhere, or
will be investigated more thoroughly in future publications.

>>>>

\begin{align}
  \pp{\MM{u}}{t} + 
  (\MM{u}\cdot\nabla)\MM{u} +
  2\MM{\Omega}\times \MM{u} + \nabla p + b\hat{\MM{k}} & = 0, \\
  \pp{p}{t} + c^2\nabla\cdot\MM{u} & = 0, \\
  \pp{b}{t} + \MM{u}\cdot\nabla b & = 0,
\end{align}
where $\MM{\Omega}$ is the rotation vector of the domain,
$\hat{\MM{k}}$ is the unit vector pointing upwards and $c$ is the
acoustic wave speed.

@@

\begin{align}
  \pp{\MM{u}}{t} + 
  (\MM{u}\cdot\nabla)\MM{u} +
  2\MM{\Omega}\times \MM{u} + c_p\theta\nabla \Pi + g\hat{\MM{k}} & = 0, \\
  \pp{\rho}{t} + \nabla\cdot(\MM{u}\rho) & = 0, \\
  \pp{\theta}{t} + \MM{u}\cdot\nabla\theta & = 0, \\
  \Pi^{(1-\kappa)/\kappa} = \frac{R}{p_0}\rho\theta, & 
\end{align}

\subsection{}

@@

\section{Results}
\label{sec: results}
The aim of this section is to present a selection of results that
demonstrate the tools available in Gusto, such as the choice of grids,
order of finite element spaces, different spatial discretisation
options, timestepping schemes and physics. The numerical properties of
these configurations (convergence, stability, accuracy and efficiency)
have either been demonstrated elsewhere, or will be investigated more
thoroughly in future publications.
